---
# This file is part of < PROJECT NAME >
# < CLASS, MODULE OR FILE NAME >
# Author(s): First Last; First Last; First Last; First Last.
# Created: 2026-01-01
# Summary: < SUMMARY OF WHAT THIS FILE OR MODULE DOES >
# Notes: See README file for documentation and full license information.
# 
# Copyright © 2026 The Regents of the University of Michigan
# 
# This program is free software: you can redistribute it and/or modify
# it under the terms of the GNU General Public License as published by
# the Free Software Foundation, either version 3 of the License, or (at your option) any later version.
# This program is distributed in the hope that it will be useful,
# but WITHOUT ANY WARRANTY; without even the implied warranty of
# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
# GNU General Public License for more details.
# You should have received a copy of the GNU General Public License along
# with this program. If not, see <https:#www.gnu.org/licenses/>.

# YAML project configuration
title: "< PROJECT NAME >"
author: "First Last; First Last; First Last; First Last."
date: "2026-01-01"
abstract: "< SUMMARY OF WHAT THIS FILE OR MODULE DOES >"
params:
  input_file: "input-data.csv"
  input_file_has_headers: TRUE
output:
  html_document:
    code_folding: show
    theme: default
    highlight: textmate
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    number_sections: true
    df_print: paged
    css: "styles/um-style.css"
    self_contained: true
---


```{r setup, include=FALSE}
# Global chunk options
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE
)
```

----

# Project Setup
## Load Required Packages
```{r load-packages}

# Load required packages
# Refer to each package for their individual license
#library(dplyr)
```

## Set Project Parameters
```{r set-parameters}
# ---- Input Parameters ----
# If using R Markdown (.Rmd), set the parameters at the top of this file in YAML.
# To re-use this script outside R Markdown, set your values here.
input_file <- if (exists("params") && !is.null(params$infile)) params$infile else "input-data.csv"
input_file_has_headers <- if (exists("params") && !is.null(params$header)) params$header else TRUE
```

## Load Data Sets
```{r load-data}
# Read in data set 
#inputData.merge <- read.csv(input_file, sep = ",", header=input_file_has_headers)

#cat("Number of rows loaded:", nrow(inputData.merge), "\n")
```

----

# Do Stuff
## Sub heading
```{r }
print('Coming soon!') # Code will be available soon.
```

## Sub heading
```{r }
print('Coming soon!') # Code will be available soon.
```


----

# Do Stuff
## Sub heading
```{r }
print('Coming soon!') # Code will be available soon.
```

## Sub heading
```{r }
print('Coming soon!') # Code will be available soon.
```



----

# License
## Copyright Notice
Copyright © 2026 The Regents of the University of Michigan


## Software and Library License Notice
This program is free software: you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation, either version 3 of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with this program. If not, see <https://www.gnu.org/licenses/gpl-3.0-standalone.html>.


## Documentation License Notice
Permission is granted to copy, distribute and/or modify this document 
under the terms of the GNU Free Documentation License, Version 1.3 
or any later version published by the Free Software Foundation; 
with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts. 
You should have received a copy of the license included in the section entitled "GNU 
Free Documentation License". If not, see <https://www.gnu.org/licenses/fdl-1.3-standalone.html>



## Citation
If you find this repository, code or paper useful for your research, please cite it.


----

Copyright © 2026 The Regents of the University of Michigan
